A simplified dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses

### 2016-09-18 Rmd/JTB_ms.tex
update notation

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A simplified dynamic bioenergetic model for coral-Symbiodinium symbioses},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header

@@

The nutritional exchange between corals and \emph{Symbiodinium} directly
underlies the capacity of corals to build coral reef ecosystems, worth
trillions of US Dollars annually (Costanza, Groot, and Sutton 2014).
However, the complex symbiotic metabolism of corals is vulnerable to
disruption by numerous anthropogenic environmental perturbations (Baker
and Cunning 2015), jeopardizing their future persistence. In order to
understand and predict coral responses to complex changes in the
environment, a mechanistic understanding of how multiple interacting
factors drive the individual and emergent physiology of both symbiotic
partners is necessary. Such a task is well suited for theoretical
modeling frameworks such as Dynamic Energy Budget (DEB) theory (Kooijman
2010), although the complexity of such theory makes these efforts
inaccessible to many biologists (Jager, Martin, and Zimmer 2013). In
order to bridge this gap, we present here a simplified dynamic
bioenergetic model for coral-\emph{Symbiodinium} symbioses that aims to
mechanistically integrate the impacts of complex environmental change on
the physiological ecology of reef corals.

@@

While the work of Muller et al. (2009) applying DEB formalism to this
system represents the most significant theoretical contribution in coral
symbiosis research to date, we aim to strengthen the role of theory and
broaden its potential application in three primary ways:

@@

In this model of coral-algal symbiosis, carbon and nitrogen are acquired
by each partner and used to construct biomass. A graphical
representation of the model is presented in Fig. 1. We use C-moles as
the unit of biomass for consistency with the rigorous mass balance of
DEB theory: 1 C-mole is equivalent to the amount of biomass containing 1
mole of Carbon atoms. Coral biomass, symbiont biomass, and prey biomass
have fixed, but different, molar N:C ratios (Table 1). Carbon and
nitrogen are combined to produce biomass by synthesizing units (SU),
which are mathematical specifications of the formation of a product from
two substrates; we use the ``parallel complementary'' formulation of
Kooijman (2010) to specify these fluxes. The two state variables in this
dynamical system are symbiont biomass and coral biomass; because
resources are acquired proportionally to surface area (and surface area
is assumed proportional to volume for corals (i.e., they are
``V1-morphs'' in DEB terminology (Kooijman 2010))), biomass increases
exponentially during growth. The rate of increase in coral biomass
(i.e.~growth) and the ratio of symbiont to host biomass are the
(i.e.~symbiosis dynamics) are the responses of interest of the system.
Below we describe the formulation of each flux involved in producing
these responses.

@@

\begin{equation} U_N = {{UN_m \cdot N} \over {N + X_{KN}}} \end{equation}

Coral biomass formation is specified by a parallel complementary SU that
combines carbon and nitrogen to form biomass. In addition to the carbon
and nitrogen acquired by direct uptake (Eqs. 1 and 2), the coral
recycles a portion of the nitrogen liberated by biomass turnover
(\(r_{NR}\)), and receives surplus fixed carbon shared by the symbiont
(\(\rho_C\)), such that the total biomass formation is specified as:

\begin{equation} Q_R = \bigg({1 \over Q_{Rm}} + {1 \over {\rho_C + U_X}} + {1 \over {(U_N + n_{NX}U_X + r_{NR})n_{NR}^{-1}}} - {1 \over {{\rho_C + U_X} + (U_N + n_{NX}U_X + r_{NR})n_{NR}^{-1}}}\bigg)^{-1} \end{equation}

where \(Q_{Rm}\) is the maximum specific growth rate. Finally, a fixed
portion of coral biomass is turned over to pay maintenance costs:

\begin{equation} T_R = \gamma_R \end{equation}

\begin{equation} {dR \over dt} = Q_R - \gamma_R \end{equation}

where \(\gamma_R\) is the parameter specifying the turnover rate.

@@

\begin{equation} \rho_N = U_N + n_{NX}U_X + r_{NR} - n_{NR}Q_R \end{equation}

Due to the inherent ``leakiness'' of the parallel complementary SU
formulation, there will always be some nitrogen shared with the symbiont
even when coral biomass formation is strongly nitrogen-limited.
Likewise, there is always a non-zero rejection flux of carbon from the
coral biomass SU, which is assumed to be lost to the environment.

@@

The symbiont produces fixed carbon through photosynthesis, a process
represented here by a single SU with two substrates: light (photons) and
inorganic carbon (CO\textsubscript{2}). The amount of light absorbed by
the symbiont depends on the scalar irradiance at the site of light
absorption, which is modified substantially relative to external
downwelling irradiance owing to multiple scattering by the coral
skeleton and self-shading by surrounding symbionts {[}Enríquez, Méndez,
and Iglesias-Prieto (2005); Wangpraseurt et al., in prep.{]}. The ratio
of internal scalar irradiance to external downwelling irradiance can
take a theoretical maximum value of 3 for a ``flat coral model''
(Marcelino et al. 2013), and may be reduced below 1 at high symbiont
densities due to self-shading. We used data from Wangpraseurt et al. (in
prep) to empirically derive this ratio as a function of symbiont density
(expressed as symbiont to host biomass ratio), and subsequently multiply
this quantity by the external downwelling irradiance \(L\) and the
effective light-absorbing surface area of symbiont biomass \(ds\) to
specify the amount of light absorbed:

\begin{equation} U_L = 3 \cdot \exp(-4.905 \cdot S/R) \cdot L \cdot ds \end{equation}

@@

\begin{equation} UCP = UCP_p + UCP_a \end{equation}

In addition to the inputs CO\textsubscript{2} specified in Eqs. 7,
additional CO\textsubscript{2} representing the metabolic production of
CO\textsubscript{2} in the host liberated from host biomass turnover
(note: recylced C from symbiont was removed so that photodamage turnover
does not make tons of C available), is made available to the
photosynthesis SU. fixed carbon is produced by the photosynthesis SU
according to:

\begin{equation} UCS = \bigg({1 \over UCS_m} + {1 \over {U_L \cdot n_{LC}}} + {1 \over {UCP + r_{CR}}} - {1 \over {U_L \cdot n_{LC} + UCP + r_{CR}}}\bigg)^{-1} \div ROS \end{equation}

where \(UCS_m\) is the maximum specific rate of photosynthesis, and
\(ROS\) is the photooxidative stress multiplier (see below). Dividing by
\(ROS\) causes the rate of photosynthesis to decline in response to
photo-oxidative stress, a phenomenon known as photoinhibition.

@@

\begin{equation} e_L = U_L - UCS \cdot n_{LC} \end{equation}

This excess light energy must be quenched by alternative pathways in
order to prevent photo-oxidative damage. \emph{Symbiodinium} may utilize
a variety of pathways for non-photochemical quenching (NPQ; Roth 2014),
which we collect in a total capacity for NPQ as a parameter of the
symbiont (\(NPQ\)). If light energy exceeds the total capacity of both
carbon fixation and NPQ, then damaging reactive oxygen species (ROS) may
be produced, which may have negative downstream consequences. We specify
a generalized photo-oxidative stress flux \(ROS\) which takes a value of
1 in the absence of stress, and increases as the amount of excess
excitation energy increases.

\begin{equation} ROS = 1 + \bigg[\bigg({{e_L/S - NPQ} \over L50}\bigg)^k\bigg]_+ \end{equation}

where \(NPQ\), \(L50\), and \(k\) are parameters of the symbiont that
determine the overall susceptibility to photo-oxidative stress.
Importantly, \(ROS\) as specified here is not a function of absolute
light absorption, but rather the amount of excess light energy \(e_L\)
after accounting for carbon fixation and NPQ. A direct consequence of
this formulation is that carbon-limitation of photosynthesis can lead to
photo-oxidative stress, a mechanism of biological importance (Wooldridge
2009) that was not captured by previous representations of
photo-oxidative stress (Eynaud, Nisbet, and Muller 2011). Moreover, this
formulation allows functional diversity among symbiont types to be
explored by changing the parameters \(NPQ\), \(L50\), and \(k\).

Carbon fixed by photosynthesis (\(UCS\)) is then used in conjunction
with nitrogen shared by the host (\(\rho_N\)) to build symbiont biomass,
following the SU equation:

\begin{equation} Q_S = \bigg({1 \over Q_{Sm}} + {1 \over UCS} + {1 \over {(\rho_N + r_{NS})n_{NR}^{-1}}} - {1 \over {UCS + (\rho_N + r_{NS})n_{NR}^{-1}}}\bigg)^{-1} \end{equation}

@@

Finally, symbiont biomass is lost at a rate of

\begin{equation} T_S = \gamma_S \cdot 5 \cdot ROS \end{equation}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{longtable}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A simplified dynamic bioenergetic model for coral-Symbiodinium symbioses},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
\usepackage{tabularx}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header
\usepackage{tabularx}

@@

The nutritional exchange between corals and \emph{Symbiodinium} directly
underlies the capacity of corals to build coral reef ecosystems, worth
trillions of US Dollars annually (Costanza, Groot, and Sutton 2014).
However, the complex symbiotic metabolism of corals is vulnerable to
disruption by numerous anthropogenic environmental perturbations,
jeopardizing their future persistence. In order to understand and
predict coral responses to complex changes in the environment, a
mechanistic understanding of how multiple interacting factors drive the
individual and emergent physiology of both symbiotic partners is
necessary. Such a task is well suited for theoretical modeling
frameworks such as Dynamic Energy Budget (DEB) theory (Kooijman 2010),
although the complexity of such theory makes these efforts inaccessible
to many biologists (Jager, Martin, and Zimmer 2013). In order to bridge
this gap, we present here a simplified dynamic bioenergetic model for
coral-\emph{Symbiodinium} symbioses that aims to mechanistically
integrate the impacts of complex environmental change on the
physiological ecology of reef corals.

@@

While the work of Muller et al. (2009) applying DEB formalism to this
system represents the most significant theoretical contribution in coral
symbiosis research to date, we aim to strengthen the role of theory and
broaden its potential application to corals in three primary ways:

@@

In this model of coral-algal symbiosis, carbon and nitrogen are acquired
by each partner and used to construct biomass. A graphical
representation of the model is presented in Fig. 1. We use C-moles as
the unit of biomass for consistency with the rigorous mass balance of
DEB theory: 1 C-mole is equivalent to the amount of biomass containing 1
mole of Carbon atoms. Host biomass (\(H\)), symbiont biomass (\(S\)),
and prey biomass (\(X\)) have fixed, but different, molar N:C ratios
(Table 1). Carbon and nitrogen are combined to produce biomass by
synthesizing units (SU), which are mathematical specifications of the
formation of a product from two substrates; we use the ``parallel
complementary'' formulation of Kooijman (2010) to specify these fluxes.
The two state variables in this dynamical system are symbiont biomass
and coral biomass; because resources are acquired proportionally to
surface area (and surface area is assumed proportional to volume for
corals (i.e., they are ``V1-morphs'' in DEB terminology (Kooijman
2010))), biomass increases exponentially during growth. The rate of
increase in coral biomass (i.e.~growth) and the ratio of symbiont to
host biomass are the (i.e.~symbiosis dynamics) are the responses of
interest of the system. Below we describe the formulation of each flux
involved in producing these responses.

Table 1

\begin{longtable}[c]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
Symbol
\strut\end{minipage} &
\begin{minipage}[b]{0.48\columnwidth}\raggedright\strut
Description
\strut\end{minipage} &
\begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
Value
\strut\end{minipage} &
\begin{minipage}[b]{0.23\columnwidth}\raggedright\strut
Units
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
N:C molar ratio in host biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.19
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
--
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
N:C molar ratio in symbiont biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.2
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
--
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NX}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
N:C molar ratio in prey biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.13
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
--
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{HT}^0\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Specific turnover rate of host biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.03
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{ST}^0\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Specific turnover rate of symbiont biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.03
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\sigma_{NH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Proportion host nitrogen turnover recycled
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.9
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
--
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\sigma_{CH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Proportion host carbon turnover recycled
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.9
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
--
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\sigma_{NS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Proportion symbiont nitrogen turnover recycled
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.9
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
--
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\sigma_{CS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Proportion symbiont carbon turnover recycled
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.9
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
--
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{Xm}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Maximum specific feeding rate of host
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.1292
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(molX \cdot CmolH^{-1} \cdot d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(K_X\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Half-saturation constant for prey uptake by host
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
20e-6
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(molX \cdot L^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{Nm}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Maximum specific DIN uptake rate by host
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.048
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(molN \cdot CmolH^{-1} \cdot d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(K_N\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Half-saturation constant for DIN uptake by host
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.46e-6
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(molN \cdot L^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{CO_2}^p\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Passive CO\textsubscript{2} delivery to symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
4.04e-3
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(molC \cdot CmolH^{-1} \cdot d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{CO_2}^a\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Active CO\textsubscript{2} delivery to symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.32--18.0
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(molC \cdot CmolH^{-1} \cdot d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{HGm}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Maximum specific growth rate of host
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
1
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{LC}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Quantum yield of photosynthesis
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.1
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(molC \cdot mol ph^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\bar{a}^*\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Effective light-absorbing cross-section of symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
1.34
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(m^2 \cdot CmolS^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{NPQ}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Non-photochemical quenching capacity of symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
40
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(mol ph \cdot CmolS^{-1} \cdot d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(k_{ROS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Excess photon energy that doubles ROS prod.
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
40-80
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(mol ph \cdot CmolS^{-1} \cdot d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(k\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Exponent on ROS production rate
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
1
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
--
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{CPm}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Maximum specific photosynthesis rate of symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
2.8
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(molC \cdot CmolS^{-1} \cdot d^{-1}\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{SGm}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.48\columnwidth}\raggedright\strut
Maximum specific growth rate of symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
0.25
\strut\end{minipage} &
\begin{minipage}[t]{0.23\columnwidth}\raggedright\strut
\(d^{-1}\)
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

Also include tables of fluxes and environmental inputs?

@@

\begin{equation} j_N = {{j_{Nm} \cdot N} \over {N + K_N}} \end{equation}

Coral biomass formation is specified by a parallel complementary SU that
combines carbon and nitrogen to form biomass. In addition to the carbon
and nitrogen acquired by direct uptake (Eqs. 1 and 2), the coral
recycles a portion of the nitrogen liberated by biomass turnover
(\(r_{NH}=\sigma_{NH}j_{HT}^0\)), and receives surplus fixed carbon
shared by the symbiont (\(\rho_C\)), such that the total biomass
formation is specified as:

\begin{equation} j_{HG} = \bigg({1 \over j_{HGm}} + {1 \over {\rho_C{S \over H} + j_X}} + {1 \over {(j_N + n_{NX}j_X + r_{NH}) / n_{NH}}} - {1 \over {{\rho_C{S \over H} + j_X} + (j_N + n_{NX}j_X + r_{NH}) / n_{NH}}}\bigg)^{-1} \end{equation}

where \(j_{HGm}\) is the maximum specific growth rate. Finally, the rate
of change in coral biomass is calculated as the specific growth rate
minum the specific biomass turnover rate (i.e., maintenance costs),
according to:

\begin{equation} {dH \over dt} = j_{HG} - j_{HT}^0 \end{equation}

@@

\begin{equation} \rho_N = j_N + n_{NX}j_X + r_{NH} - n_{NH}j_{HG} \end{equation}

Due to the inherent inefficiency of the parallel complementary SU
formulation, there will always be some nitrogen shared with the symbiont
even when coral biomass formation is strongly nitrogen-limited.
Likewise, there is always a non-zero rejection flux of carbon from the
coral biomass SU, which is assumed to be lost to the environment.

@@

The symbiont produces fixed carbon through photosynthesis, a process
represented here by a single SU with two substrates: light (photons) and
inorganic carbon (CO\textsubscript{2}). The amount of light absorbed by
the symbiont depends on the scalar irradiance at the site of light
absorption, which is modified substantially relative to external
downwelling irradiance owing to multiple scattering by the coral
skeleton and self-shading by surrounding symbionts (Enríquez, Méndez,
and Iglesias-Prieto 2005; Marcelino et al. 2013). We used data from
Marcelino et al. (2013) to empirically derive the ratio of internal
scalar irradiance to external downwelling irradiance as a function of
symbiont density (expressed as symbiont to host biomass ratio), and
subsequently multiply this quantity by the external downwelling
irradiance \(L\) and the effective light-absorbing surface area of
symbiont biomass \(ds\) to specify the amount of light absorbed:

\begin{equation} j_L = \big[1.26 + 1.39 \cdot \exp(-6.48 \cdot {S \over H})\big] \cdot L \cdot \bar{a}^* \end{equation}

@@

\begin{equation} j_{CO_2} = j_{CO_2}^p + j_{CO_2}^a \end{equation}

In addition to the inputs CO\textsubscript{2} specified in Eqs. 7,
additional CO\textsubscript{2} representing the metabolic production of
CO\textsubscript{2} from host and symbiont biomass turnover
(\(r_{CH}=\sigma_{CH}j_{HT}^0; r_{CS}=\sigma_{CS}j_{ST}^0\)) is made
available to the photosynthesis SU. fixed carbon is produced by the
photosynthesis SU according to:

\begin{equation} j_{CP} = \bigg({1 \over j_{CPm}} + {1 \over {n_{LC} j_L }} + {1 \over {(j_{CO_2} + r_{CH}){H \over S} + r_{CS}}} - {1 \over {n_{LC} j_L + (j_{CO_2} + r_{CH}){H \over S} + r_{CS}}}\bigg)^{-1} \div c_{ROS} \end{equation}

where \(j_{CPm}\) is the maximum specific rate of photosynthesis, and
\(c_{ROS}\) is the photooxidative stress multiplier (see below).
Dividing by \(c_{ROS}\) causes the rate of photosynthesis to decline in
response to photo-oxidative stress, a phenomenon known as
photoinhibition.

@@

\begin{equation} j_{eL} = j_L - j_{CP} / n_{LC} \end{equation}

This excess light energy must be quenched by alternative pathways in
order to prevent photo-oxidative damage. \emph{Symbiodinium} may utilize
a variety of pathways for non-photochemical quenching (NPQ; Roth 2014),
which we collect in a total capacity for NPQ as a parameter of the
symbiont (\(j_{NPQ}\)). If light energy exceeds the total capacity of
both carbon fixation and NPQ, then damaging reactive oxygen species
(ROS) may be produced. We represent this as a scaled flux of ROS
\(c_{ROS}\), which takes a value of 1 when all light absorbed is
quenched by photochemistry and NPQ, and increases as the amount of
excess excitation energy increases.

\begin{equation} c_{ROS} = 1 + \bigg[\bigg({{j_{eL} - j_{NPQ}} \over k_{ROS}}\bigg)^k\bigg]_+ \end{equation}

where \(j_{NPQ}\), \(k_{ROS}\), and \(k\) are parameters of the symbiont
that determine the onset and rate of ROS production. Importantly,
\(c_{ROS}\) as specified here is not a function of absolute light
absorption, but rather the amount of excess light energy \(j_{eL}\)
after accounting for carbon fixation and NPQ. A direct consequence of
this formulation is that carbon-limitation of photosynthesis can lead to
photo-oxidative stress, a mechanism of biological importance (Wooldridge
2009) that was not captured by previous representations of
photo-oxidative stress (Eynaud, Nisbet, and Muller 2011). Moreover, this
formulation allows functional diversity among symbiont types to be
explored by changing the parameters \(j_{NPQ}\), \(k_{ROS}\), and \(k\).

Carbon fixed by photosynthesis (\(j_{CP}\)) is then used in conjunction
with nitrogen shared by the host (\(\rho_N\)) and a proportion of
nitrogen recycled from symbiont biomass turnover
(\(r_{NS}=\sigma_{NS}j_{ST}^0\)) to build new symbiont biomass,
following the SU equation:

\begin{equation} j_{SG} = \bigg({1 \over j_{SGm}} + {1 \over j_{CP}} + {1 \over {(\rho_N{H \over S} + r_{NS}) / n_{NH}}} - {1 \over {j_{CP} + (\rho_N{H \over S} + r_{NS}) / n_{NH}}}\bigg)^{-1} \end{equation}

@@

Symbiont biomass turnover includes a component of constant turnover
specified by the parameter \(j_{ST}^0\), representing fixed maintenance
costs, plus a component that scales with the magnitude of ROS
production.

\begin{equation} j_{ST} = j_{ST}^0(1 + 5 \cdot (c_{ROS}-1)) \end{equation}

This second component of symbiont biomass loss can represent both
photodamage and/or symbiont expulsion (i.e., bleaching), both of which
happen in response to higher levels or ROS production. The constant 5 is
included to increase biomass loss in response to ROS. (Note that
recycling of symbiont biomass turnover (\(rNS\) and \(rCS\)) only occurs
based on the basal maintenance related turnover (i.e., \(j_{ST}^0\)),
and not the bleaching-related biomass loss, as this loss represents
biomass being damaged or being expelled from the holobiont). Finally,
the balance equation representing the change in symbiont biomass over
time can be specified as the growth rate minus the turnover rate:

\begin{equation} {dS \over dt} = j_{SG} - j_{ST} \end{equation}
